\begin{thebibliography}{10}

\bibitem{ATLASSummaryPlots}
ATLAS~Collaboration. 
Standard Model summary plots. 
{\em ATLAS Public Note ATL-PHYS-PUB-2024-011}, 2024.

%\cite{CERN:1992jvx}
\bibitem{CERN:1992jvx}
ATLAS~Collaboration
ATLAS: Letter of intent for a general purpose p p experiment at the large hadron collider at CERN.
{\em CERN-LHCC-92-04}, 1992.

\bibitem{Aad2024}
ATLAS~Collaboration. 
The ATLAS experiment at the CERN Large Hadron Collider: a description of the detector configuration for Run~3. 
{\em JINST}, 19:P05063, 2024.
URL: \url{http://dx.doi.org/10.1088/1748-0221/19/05/P05063}

\bibitem{Mann:2010nvj}
R.~Mann. 
\emph{An Introduction to Particle Physics and the Standard Model}. 
Taylor \& Francis, 2010. 
ISBN~978-1-4200-8300-2.

%12 citations counted in INSPIRE as of 09 Oct 2025
\bibitem{SM-Wikipedia}
Wikipedia. 
Elementary particle. 
URL: \url{https://en.wikipedia.org/wiki/Elementary_particle}. 
Accessed: October 9, 2025.

\bibitem{YangMills1954}
C.~N.~Yang and R.~L.~Mills. 
Conservation of isotopic spin and isotopic gauge invariance. 
\emph{Phys. Rev.}, 96:191--195, 1954.

\bibitem{Higgs1964a}
P.~W.~Higgs. 
Broken symmetries, massless particles and gauge fields. 
\emph{Phys. Lett.}, 12:132--133, 1964. 
DOI: \href{https://doi.org/10.1016/0031-9163(64)91136-9}{10.1016/0031-9163(64)91136-9}.

\bibitem{Higgs1964b}
P.~W.~Higgs. 
Broken symmetries and the masses of gauge bosons. 
\emph{Phys. Rev. Lett.}, 13:508--509, 1964. 
DOI: \href{https://doi.org/10.1103/PhysRevLett.13.508}{10.1103/PhysRevLett.13.508}.

\bibitem{EnglertBrout1964}
F.~Englert and R.~Brout. 
Broken symmetry and the mass of gauge vector mesons. 
\emph{Phys. Rev. Lett.}, 13:321--323, 1964. 
DOI: \href{https://doi.org/10.1103/PhysRevLett.13.321}{10.1103/PhysRevLett.13.321}.

\bibitem{GuralnikHagenKibble1964}
G.~S.~Guralnik, C.~R.~Hagen, and T.~W.~B.~Kibble. 
Global conservation laws and massless particles. 
\emph{Phys. Rev. Lett.}, 13:585--587, 1964. 
DOI: \href{https://doi.org/10.1103/PhysRevLett.13.585}{10.1103/PhysRevLett.13.585}.

\bibitem{Higgs1966}
P.~W.~Higgs. 
Spontaneous symmetry breakdown without massless bosons. 
\emph{Phys. Rev.}, 145:1156--1163, 1966. 
DOI: \href{https://doi.org/10.1103/PhysRev.145.1156}{10.1103/PhysRev.145.1156}.

\bibitem{ATLASHiggs}
ATLAS Collaboration.
Observation of a new particle in the search for the Standard Model Higgs boson with the ATLAS detector at the LHC. 
\emph{Physics Letters B} 716.1 (2012), pp. 1-29

\bibitem{CMSHiggs}
CMS Collaboration
Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC.
\emph{Physics Letters B} 716.1 (Sept. 2012), pp. 30-61

\bibitem{EvansBryant2008}
L.~Evans and P.~Bryant. 
LHC machine. 
\emph{JINST}, 3:S08001, 2008.

\bibitem{Lopienska}
E.~Lopienska.
The CERN accelerator complex layout in 2022. Complexe des accelerateurs du CERN en janvier 2022.
\emph{CERN-GRAPHICS-2022-001}, 2022. 
URL: \url{https://cds.cern.ch/record/2800984}

\bibitem{ATLASSchematics}
J.~Pequenao
Computer generated image of the whole ATLAS detector.
\emph{CERN-GE-0803012}, 2008.
URL: \url{https://cds.cern.ch/record/1095924}

\bibitem{ATLASID}
J.~Pequenao
Computer generated image of the ATLAS inner detector.
\emph{CERN-GE-0803014}, 2008.
URL: \url{https://cds.cern.ch/record/1095926}

\bibitem{Calorimeters}
J.~Pequenao
Computer generated image of the ATLAS Liquid Argon.
\emph{CERN-GE-0803016}, 2008.
URL: \url{https://cds.cern.ch/record/1095928}

\bibitem{MuonSpectrometer}
J.~Pequenao
Computer generated image of the ATLAS Muons subsystems.
\emph{CERN-GE-0803017}, 2008.
URL: \url{https://cds.cern.ch/record/1095929}

\bibitem{JCatmore}
J.~Catmore
The ATLAS data processing chain: from collision to paper.
Joint Oslo/Bergen/NBI ATLAS Software Tutorial. University of Oslo, 2016.
URL: \url{https://indico.cern.ch/event/472469/contributions/1982677/attachments/1220934/1785823/intro_slides.pdf}

\bibitem{ROOTTTree}
ROOT by CERN.
TTree Class Reference.
\emph{ROOT Reference Guide}.
URL: \url{https://root.cern.ch/doc/v630/classTTree.html}

\bibitem{Serhan}
A.~Serhan~Mete,M.~Nowak,P.~van~Gemmeren
Persistifying the Complex Event Data Model of the ATLAS Experiment in RNTuple. 
\emph{22nd International Workshop on Advanced Computing and Analysis Technique in Physics Research}. 11-15 March 2024. 

\bibitem{RNTupleSpecs2025}
ROOT Team Collaboration
RNTuple Binary Format Specification 1.0.0.0
\emph{CERN-OPEN-2025-001} (2024)

\bibitem{Blomer2020}
J.~Blomer,P.~Canal,A.~Naumann,D.~Piparo
Evolution of the ROOT TreeI\/O
\emph{EPJ Web of Conf}.245 (2020) 02030

\bibitem{GoogleCloud}
Google Cloud
What is binary large object (BLOB) storage?
URL: \url{https://cloud.google.com/discover/what-is-binary-large-object-storage}

\bibitem{smartpointer}
Wikipedia
Smart pointer
URL: \url{https://en.wikipedia.org/wiki/Smart_pointer}

\bibitem{ROOT}
ROOT Team
ROOT Reference Documentation
URL: \url{https://root.cern.ch/doc/master/index.html}

\bibitem{RNTuple:ParquetHDF5}
J.~Lopez-Gomez, J.~Blomer
RNTuple performance: Status and Outlook
\emph{J. Phys. Conf. Ser.}2438 (2023) 1, 012118

\bibitem{LHCDesignReport}
O.~S.~Bruning, P.~Collier,P.~Lebrun,S.~Myers,R.~Ostojic,J.~Poole,P.~Proudlock
LHC Design Report
\emph{Geneva:CERN},2024-548

\bibitem{ATLASOpenData}
ATLAS Collaboration
URL: \url{https://opendata.atlas.cern/}

\bibitem{ATHENA}
The ATLAS Collaboration.
Athena
\emph{Zenodo}, (2019)
DOI: \url{https://doi.org/10.5281/zenodo.2641996}

\bibitem{ROOTsRNTuple}
J.~Blomer,P.~Canal,F.~de~Geus,J.~Hahnfeld,A.~Naumann,J.~Lopez-Gomez,G.~Lazzari~Miotto,V.~E.~Padulano
ROOT's RNTuple I\/O Subsystem:The Path to Production
\emph{EPJ Web of Conf}.295, 06020 (2024)

\bibitem{AGC}
Iris HEP
Analysis Grand Challenge
URL: \url{https://iris-hep.org/projects/agc.html:S}

\bibitem{ATLAS_website}
ATLAS Collaboration.
The ATLAS Experiment: Trigger and Data Acquisition
URL: \url{https://atlas.cern/Discover/Detector/Trigger-DAQ}

\bibitem{HL-LHC}
I. Bejar Alonso et al. 
"High-Luminosity Large Hadron Collider (HL-LHC): Technical design report.""
\emph{CERN Yellow Reports} Vol. 10 (2020)

\bibitem{invariant_mass}
ATLAS Collaboration
"Mass/Invariant mass"
URL: \url{https://atlas.cern/glossary/mass}

\bibitem{4-vectors}
ATLAS Collaboration
Facts Sheets
"4-Vectors and particle mass"
URL: \url{https://cds.cern.ch/record/2919871/files/4-vectors%20and%20invariant%20mass%20cheat%20sheet.pdf}

\bibitem{HL-LHC_ATLAS_CMS}
The ATLAS and CMS Collaborations. 
Highlights of the HL-LHC physics projections by ATLAS and CMS.
\emph{CMS-HIG-25-002} 2025

\bibitem{InnerTracker}
ATLAS Collaboration
Technical Design Report for the ATLAS Inner Tracker Pixel Detector, 
\emph{CERN-LHCC-2017-021}, 2017.

\bibitem{HGTD}
ATLAS Collaboration
Technical Design Report: A High-Granularity Timing Detector for the ATLAS Phase-II Upgrade. 
\emph{CERN-LHCC-2020-007}, 2020

\bibitem{MuonChamber}
ATLAS Collaboration
Technical Design Report for the Phase-II Upgrade of the ATLAS Muon Spectrometer.
\emph{CERN-LHCC-2017-017}, 2017. 

\bibitem{LAr}
ATLAS Collaboration.
ATLAS Liquid Argon Calorimeter Phase-II Upgrade : Technical Design Report.
\emph{CERN-LHCC-2017-018}, 2017

\bibitem{TileCalo}
ATLAS Collaboration.
Technical Design Report for the Phase-II Upgrade of the ATLAS Tile Calorimeter.
\emph{CERN-LHCC-2017-019}, 2017.

\bibitem{MuonSpecup}
ATLAS Collaboration. 
Technical Design Report for the Phase-II Upgrade of the ATLAS Tile Calorimeter.
\emph{CERN-LHCC-2017-019}, 2017.

\bibitem{TDAQ}
ATLAS Collaboration
Technical Design Report for the Phase-II Upgrade of the ATLAS TDAQ System. 
\emph{CERN-LHCC-2017-020}, 2017 

\bibitem{LHCb}
S.~Amato et al. 
LHCb technical proposal
\emph{CERN-LHCC-98-04}

\bibitem{ALICE}
ALICE Collaboration
ALICE: Technical proposal for a Large Ion collider Experiment at the CERN LHC
\emph{Geneva: CERN}, 1995 - 237

\bibitem{Iris-HEP}
URL: \url{https://iris-hep.org/}

\bibitem{AGC}
URL: \url{https://iris-hep.org/projects/agc.html}

\bibitem{Alex}
URL: \url{https://github.com/alexander-held/PyHEP-2022-AGC/blob/main/talk.ipynb}

\end{thebibliography}
